%! TEX root='..\main.tex'

\section{Response Posts}
  \subsection{Response 2}
    \begin{quotation}
      My name is Kristyna Sekera, and I am from Denver, Colorado. I am currently
        attending Red Rocks Community College. I am completing my general
        courses right, as I do not have a set major. After graduation, I hope
        to be able to travel and see the world. I enrolled in interpersonal
        communication because it seemed the most interesting to me, as well as
        being heavily applicable to my daily life. This is my second year taking
        online classes, so I am pretty comfortable with them. My hobbies include
        traveling, drawing, and snowboarding. My favorite travel destinations
        are the Czech Republic and Croatia. I am a little biased towards Czech,
        since my family is from there, but it is, without a doubt, one of my
        favorite places to visit. I don’t really have a favorite quote, but I
        like the quotes that outline living your life to the fullest extent. I
        keep a notebook that has the assignments and due dates listed, and I
        find that helps me in submitting my work on time.

      A time I can think of when one of my texts was completely misconstrued by
        the recipient, was when my dad’s former girlfriend asked my sister and
        me to pick up some food for dinner. She asked me if we could pick it up,
        if she ordered it. I am not entirely sure what I replied, but it was
        along the lines of an “okay”. She then got upset, thinking that we did
        not want to go pick up the food and have dinner. The problem lied with
        her interpretation of the message, but the fact that it was via text
        also had an impact on the understanding. The fact that you cannot pick
        up on people’s body language and visual cues, over the phone, leads to
        a lot of misinterpretation. I could have added an exclamation point, or
        used a different phrase, that would have indicated that I did not mind
        going to get the food. I have learned from that experience, when
        communicating over the phone, I find it really important to use
        punctuation marks, as they can give the other person a clue on how to
        interpret your message.
    \end{quotation}

    \paragraph{This is a response to Kristyna Sekera with Post ID 43156527}
      Hello, Kristyna! I notice you mentioned drawing as one of your hobbies,
        if not too much to ask I would \textit{love} to see some of your
        artwork! I have always wanted to visited the Czech Republic, but never
        met anyone from there! I took a few Czech classes in Atlanta before I
        moved to Colorado and have yet to get the chance to make the trip.

      That situation of the misunderstanding over text message sounds horrible!
        I did not see anything wrong with your reply of ``okay'' for something
        like a task given to you. Usually, ``okay'' is a word which has
        intonations of agreement rather than the opposite!
