\documentclass[stu,12pt]{apa7}
  \usepackage{times}
  \usepackage[english]{babel}
  \usepackage[utf8]{inputenc}
  \usepackage{xcolor}
  \usepackage{hyperref}
  \usepackage{enumitem}
  \usepackage{geometry}
  \usepackage{soul}
  \usepackage{graphicx}
  \usepackage{csquotes}
  \usepackage{bookmark}
  \usepackage{mdframed}
  \usepackage[toc]{appendix}
  % \usepackage[backend=biber,style=apa]{biblatex}
  \usepackage{fancyhdr}
  \usepackage{mdframed}

  % Bibliography Setup
  % \addbibresource{main.bib}

  % Hyperlink Setup
  \hypersetup{
    colorlinks = true,
    urlcolor = blue,
    linkcolor = blue,
    citecolor = blue
  }

  % Page and Text Layout
  \geometry{%
    a4paper,%
    top=1in,%
    bottom=1in,%
    left=1in,%
    right=1in%
  }
  \setlength{\headheight}{15pt}

  % Header
  \lhead{COM120CG1-M1D0}

  % Title Page
  \title{%
    M1D0: Student Introductions
  }
  \shorttitle{Module 1 Discussion 0}
  \author{Ashton Hellwig}
  \authorsaffiliations{Department of Mathematics, Front Range Community College}
  \course{COM115: Interpersonal Communication}
  \professor{Richard Thomas}
  \duedate{November 07, 2020 23:59:59 MDT}
  \date{\today}
  \abstract{%
    \textbf{Overview}\\%
    Welcome to COM 125—Interpersonal Communication!\\%

    The first Module 1 Discussion is titled, ``Student Icebreaker\\%
      (Introductions)''. Getting to know your classmates early on contributes to
      building a sense of community in our class.

    Read and comply with instructions 1, 2, 3, 4, and 5 appearing below.
  }

\begin{document}
  % Title Page
  \maketitle

  % Initial Post
  \section{Initial Post}
    \subsection*{Instructions}
      \begin{enumerate}
        \item Introduce yourself by name and location. Then, state your major,
          home college, career goals following graduation, why you enrolled in
          our online class (in addition to it being required), your experience
          with online classes, hobbies, favorite travel destination, favorite
          quote, how you intend to make time for completing and submitting
          classwork in accordance with due dates appearing in the Course
          Schedule, and anything else to help us get to know you better.
        \item Describe a time you communicated something via social media, text,
          or email that was completely misunderstood by the recipient.
        \item Reply to the following questions:
          \begin{itemize}
            \item Where did the problem lie, with your communication or with
              their interpretation?
            \item How did the nature of the communication (electronic versus
              face-to-face) impact understanding?
            \item What could you have done differently that would have changed
              the outcome of the communication?
            \item How have you applied what you learned from that experience to
              your communication?
          \end{itemize}
        \item Include a minimum of 100 words in your Introduction. Add a word
          count to the end of your Introduction.
        \item Finally, read the Introduction submitted by at least two
          classmates. Submit a welcome message in a reply to the Introduction
          submitted by two classmates. Remember to read and comply with the
          Class Netiquette Instructions message posted in this Discussion. You
          can do this!
      \end{enumerate}

    % Introduction
    \newpage
    \subsection{Introduction}
      This is just a simple little placeholder.


    % Replies
    % \include{tex/replies.tex}
\end{document}
